Extracting sunbeams from cucumbers: Computational reproducibility is essential for archaeological science

### 2025-05-17 README.Rmd
update readme

-   [:file_folder: paper](/analysis/paper): Quarto source document for
    manuscript. Includes code to reproduce the figures and tables
    generated by the analysis.
-   [:file_folder: data](/analysis/data): Data used in the analysis.
-   [:file_folder: figures](/analysis/figures): Plots and other
    illustrations

@@

1. Install [Docker](https://www.docker.com/get-started/) on your computer 
2. Download the compendium, e.g. from GitHub by clicking on the green `< > Code` button above, then click `Download ZIP`, then unzip on your computer
3. Set your terminal working directory to the compendium, and run `docker build -t wos .` to build the container on your computer, it will take a few minutes and require an internet connection.
4. Run in your terminal `docker run --rm -it -e ROOT=TRUE -e PASSWORD=rstudio -dp 8787:8787 wos` to start the container on your computer
5. Go to http://localhost:8787/ with your browser and enter `rstudio` in both fields to start RStudio in your browser, running in the Docker container with all the required depedencies installed
6. In RStudio, run `rstudioapi::openProject("/home/rstudio/web-of-science-archaeology")` to open the compendium's project
7. Run ` rmarkdown::render("analysis/paper/paper.qmd", output_dir='/tmp')` to render the Quarto document that is the manuscript submitted for publication
8. After the code has executed, view the rendered output document by running `browseURL("/tmp/paper.html")`
8. When finished, to delete the Docker container from your computer, run this in the terminal `docker ps -aq | xargs docker stop | xargs docker rm`

>>>>

-   [:file_folder: paper](/analysis/paper): Quarto source documents for the 
    **manuscript** and **supplementary document** on GAMs. Includes code to 
    reproduce the figures and tables generated by the analysis.
-   [:file_folder: data](/analysis/data): Data used in the analysis.
-   [:file_folder: figures](/analysis/figures): Plots and other
    illustrations

@@

1. Install [Docker](https://www.docker.com/get-started/) on your computer 
2. Download the compendium, e.g. from GitHub by clicking on the green `< > Code` button above, then click `Download ZIP`, then unzip on your computer
3. Set your terminal working directory to the compendium, and run `docker build -t wos .` to build the container on your computer, it will take a few minutes and require an internet connection.
4. Run in your terminal `docker run --rm -it -e ROOT=TRUE -e PASSWORD=rstudio -dp 8787:8787 wos` to start the container on your computer
5. Go to http://localhost:8787/ with your browser and enter `rstudio` in both fields to start RStudio in your browser, running in the Docker container with all the required depedencies installed
6. In RStudio, run `rstudioapi::openProject("/home/rstudio/web-of-science-archaeology")` to open the compendium's project. This project uses [`renv`](https://rstudio.github.io/renv/) to document and manage dependencies, this will be activated when the project is first opened in RStudio. 
7. Run ` rmarkdown::render("analysis/paper/paper.qmd", output_dir='/tmp')` to render the Quarto document that is the manuscript submitted for publication
8. After the code has executed, view the rendered output document by running `browseURL("/tmp/paper.html")`
8. When finished, to delete the Docker container from your computer, run this in the terminal `docker ps -aq | xargs docker stop | xargs docker rm`
